---
title: "Weather Information Preferences in the United States"
subtitle: "Summary Report for the `r params$region` Region"
author: "Author: Elizabeth Juhasz"
date: "`r format(Sys.Date(), '%A, %B %d, %Y') `"
output: 
  ioslides_presentation:
    logo: images/sunstar.png
      
params:
  region: 
    label: "Region:"
    value: Mountain
    input: select
    choices: ["East North Central","East South Central", 
    "Middle Atlantic","Mountain", "New England", 
    "Pacific","South Atlantic", "West North Central",
    "West South Central"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


```{r, echo=FALSE, message=FALSE, warning=FALSE }
knitr::read_chunk("code/setup.R")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r loadData}
```


```{r child="text/backgroundSection.Rmd"}
```

 
```{r child="text/purposeSection.Rmd"}
```




## Demographic Summary Tables


## _OPTIONAL_ Demographics of Survey Respondents in a Merged Table

This section is provided as an example of how to merge the three demographic summary tables for the `r nrow(sdat)` survey respondents.
```{r makeTable, code=readLines("code/makeTable.R")}

```

## Weather Source Preference by Gender

Finally, here is a breakdown of the `r nrow(sdat)` survey respondents for the `r params$region` region of the US on how they check their daily weather by gender.

```{r}
knitr::read_chunk("code/makeChart.R")
```

```{r makeCharts}
```


